FTLR proof cases

### 2018-04-25 fully-abstract-comp/ftlr-proof-cases.tex
updated assumptions of FTLR proof

\maketitle
\section{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[non-expansiveness of relations]
  \label{lem:non-expansive}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{(b,e)}\readCond{\lin}{W}$, then $\npair[n']{(b,e)}\readCond{\lin}{W}$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$.
  \end{itemize}
\end{lemma}

\begin{lemma}[World monotonicity of relations]
  \label{lem:monotonicity}
  For all $n$, $W' \future W$, we have that
  \begin{itemize}
  \item If $(w_1,w_2) \in H_\sigma~\sigma~W$, then $(w_1,w_2) \in H_\sigma~\sigma~W'$.
  \item If $\npair{(w_1,w_2)} \in \lrv(W)$, then $\npair{(w_1,w_2)} \in
    \lrv(W')$.
\end{itemize}
\end{lemma}

@@

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}
\begin{proof}
  Follows easily by inspecting the definitions of $\lrv$, $\readCond$, $\addressable$, $\writeCond$, $\execCond$ and $\xReadCond$ and using Lemma~\ref{lem:purePart-idempotent}.
\end{proof}

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \begin{array}{l}
  \npair{(\baddr,\eaddr)}\in \readCond{\lin,W}\\
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
  \end{array}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ 
\dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\lau{$(c,c)$ is not shown or assumed to be in the value relation, so to make sure it respects lineraity, this condition is placed here. Further, this does become a proof obligation when you use the FTLR.}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
That is, let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

{\color{DarkGreen}
\dominique{Proposed proof refactoring below:}
First, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz, xjmp
\end{itemize}

@@

}

>>>>

\maketitle
\section{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[non-expansiveness of relations]
  \label{lem:non-expansive}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{(b,e)} \in \readCond{\lin,W}$, then $\npair[n']{(b,e)} \in \readCond{\lin,W}$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$.
  \end{itemize}
\end{lemma}

\begin{lemma}[World monotonicity of relations]
  \label{lem:monotonicity}
  For all $n$, $W' \future W$, we have that
  \begin{itemize}
  \item If $(w_1,w_2) \in H_\sigma~\sigma~W$, then $(w_1,w_2) \in H_\sigma~\sigma~W'$.
    \lau{This should hold for any valid $H_\sigma$, but we need to prove it for specific instantiations.}
  \item If $\npair{(w_1,w_2)} \in \lrv(W)$, then $\npair{(w_1,w_2)} \in
    \lrv(W')$.
\end{itemize}
\end{lemma}

@@

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}
\begin{proof}
  Follows easily by inspecting the definitions of $\lrv$, $\readCond[]{}$, $\addressable{}$, $\writeCond[]{}$, $\execCond[]{}$ and $\xReadCond[]{}$ and using Lemma~\ref{lem:purePart-idempotent}.
\end{proof}

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
  \begin{itemize}
  \item $\trust = \trusted \vee \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{enumerate}[label={\roman*)}]
  \item \begin{itemize}
    \item $W \vdash_{(\ta,\stkb)} (\mscode,\_,\_,\_,\sigrets,\sigcloss)$
    \item $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \trusted$
    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \begin{itemize}           
      \item $\src{\Phi}$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
      \item $\src{\Phi}$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
      \item $\src{\Phi}$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
      \item $\src{\Phi}$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{enumerate}
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lreg{\trust}(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and pick
\begin{itemize}
\item $\Phi_S' = \xjumpResult{c}{c}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{c}{c}{\Phi_T}$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S',\Phi_T')} \in \lro
\]
In order to do this, we first, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz, xjmp
\end{itemize}

@@
